Decomposing biodiversity change to processes of extinction, colonization, and persistence across scales

### 2023-05-17 scripts/ms_scaling_changes.qmd
updating code

The data provided (*i.e.* CzAtlas and CzBBS) are already processed into species richness, colonization, extinction... per unit of area. If you are interested in accessing the raw datasets, feel free to contact the following email address: leroy\@fzp.czu.cz.

>>>>

The data used (*i.e.* CzAtlas and CzBBS) are not open thus we provide them already processed into species richness, colonization, extinction... per unit of area. If you are interested in accessing the raw datasets (with species identities), feel free to contact the following email address: leroy\@fzp.czu.cz.
